Regime transition identification for water governance at a basin scale

### 2020-11-24 tex/main/manuscript.tex
amend figure captions

% 这一节主要展示IWGI的变化趋势和WUR的划分
With two significant points, the changes of IWGI are detected into three periods (Figure~\ref{fig:IWGI}A). 
Not only the slope of trends are various within each period (Figure~\ref{fig:IWGI}B), changes are also mainly contributed by different water governance dimensions (Figure~\ref{fig:IWGI}C).
% 第一阶段
In the first period (P1, 1965-1978), the IWGI had a rapidly increasing and the supply made the most striking positive contribution (131\%), while purpose and allocation had slight negative contribution (-11\% and -20\%).
% 第二阶段
In the second period (P2, 1979-1994), though contributions of purpose and allocation turned into positive, the IWGI experienced a drop because huge-declined supply capacity plays a larger negative role (-188\% dropped than P1). 
% 第三阶段
However, as the further increasing of positive contributions of purpose (75\%) and allocation (84\%), and decreases of water supply in negative contribution (-59\%) in the third period (P3, 1995-2013), a positive growth of the IWGI returned.

>>>>

% 这一节主要展示IWGI的变化趋势和WUR的划分
With two significant points, the changes of IWGI are detected into three periods (Figure~\ref{fig:IWGI}A). 
Not only the slope of trends are various within each period, changes are also mainly contributed by different water governance dimensions (Figure~\ref{fig:IWGI}B).
% 第一阶段
In the first period (P1, 1965-1978), the IWGI had a rapidly increasing and the supply made the most striking positive contribution (131\%), while purpose and allocation had slight negative contribution (-11\% and -20\%).
% 第二阶段
In the second period (P2, 1979-1994), though contributions of purpose and allocation turned into positive, the IWGI experienced a drop because huge-declined supply capacity plays a larger negative role (-188\% dropped than P1). 
% 第三阶段
However, as the further increasing of positive contributions of purpose (75\%) and allocation (84\%), and decreases of water supply in negative contribution (-59\%) in the third period (P3, 1995-2013), a positive growth of the IWGI returned.
